Selecting and ranking interesting pairs of cyclic temporal granularities

### 2020-12-10 paper/main.Rmd
pdf update

Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets. Let the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}, b_{k})$ be denoted as $d_{(jk, j', k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$. Pairwise distances could be within-facets or between-facets. Figure \ref{fig:distance-explain} illustrates how the within-facet or between-facet distances are defined. Pairwise distances are within-facets ($d_{w}$) when $b_{k} = b_{k'}$, that is, between pairs of the form $(a_{j}b_{k}, a_{j'}b_{k})$ as shown in panel (3) of Figure \ref{fig:distance-explain}. If categories are ordered (like all temporal cyclic granularities), then only distances between pairs where $a_{j'} = (a_{j+1})$ are considered (panel (4)). Pairwise distances are between-facets ($d_{b}$) when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.

@@

\begin{equation}
d*_{(j,k), (j'k')} =
\begin{cases}
\lambda d_{(j,k), (j'k')},& \text{if } d = d_w\\
(1-\lambda)  d_{(j,k), (j', k')},              & \text{if } d = d_b\\
\end{cases}
\end{equation}

The maximum weighted pairwise distances are defined as:
$$WPD = max_{j, j', k, k'}(d*_{(j,k), (j', k')})
\forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$.

@@

**Objective:** 1. Behavior of wpd under different null designs N(0,1), N(5, 1), N(0,5) and N(5,5), Gamma(0,1), Gamma(0, 0.2) for different nx and nfacets. Here, we have to fix a value of lambda = 0.67.

@@

```{r}

```{r}

### Choice of alternate designs

A normal distribution is taken for this purpose. We would calibrate the values of $WPD$ for different designs illustrated in Section \ref{sec:idea}.

$$\mu_{j.} = \mu + j\omega$$
or, $$\mu_{.k} = \mu + k\omega$$ where,   
$j$ and $k$ are the index of the x and facet category respectively 
$\mu$ is the mean of the first category and $\omega$ is the increment from the starting value.

mean = 0
range_mean = c(0, 1, 3,  5, 7, 15, 20)
sd = 1
range_sd = c(1, 3,  5, 7, 15, 20)
range_w =  c(1, 2, 3, 4, 5)
range_lambda = seq(0.1, 0.9, 0.05)

@@

```{r tuning-one-omega}
knitr::include_graphics(here::here("simulations/tuning_param/figs/intersection_plot.png"))
```

>>>>

Consider two cyclic granularities $A$ and $B$, such that $A = \{ a_j: j = 1, 2, \dots, J\}$ and $B = \{ b_k: k = 1, 2, \dots, K\}$ with $A$ placed across x-axis and $B$ across facets. Let the pairwise distances between pairs $(a_{j} b_{k}, a_{j'}, b_{k})$ be denoted as $d_{(jk, j'k')} = JSD(a_{j}b_{k}, a_{j'}b_{k'})$. Pairwise distances could be within-facets or between-facets. Figure \ref{fig:distance-explain} illustrates how the within-facet or between-facet distances are defined. Pairwise distances are within-facets ($d_{w}$) when $b_{k} = b_{k'}$, that is, between pairs of the form $(a_{j}b_{k}, a_{j'}b_{k})$ as shown in panel (3) of Figure \ref{fig:distance-explain}. If categories are ordered (like all temporal cyclic granularities), then only distances between pairs where $a_{j'} = (a_{j+1})$ are considered (panel (4)). Pairwise distances are between-facets ($d_{b}$) when they are considered between pairs of the form $(a_{j}b_{k}, a_{j}b_{k'})$.

@@

\begin{equation}
d*_{(j,k), (j'k')} =
\begin{cases}
\lambda d_{(jk), (j'k')},& \text{if } d = d_w\\
(1-\lambda)  d_{(jk), (j'k')},              & \text{if } d = d_b\\
\end{cases}
\end{equation}

The maximum weighted pairwise distances are defined as:
$$WPD = max_{j, j', k, k'}(d*_{(jk), (j'k')})
\forall j, j' \in \{1, 2, \dots, J\}, k, k' \in \{1, 2, \dots, K\}$$.

@@

**Objective:** 1. Behavior of wpd under different null designs N(0,1), N(5, 1), Gamma(0.5,1), Gamma(2,1) for different nx and nfacets. Here, we have to fix a value of lambda = 0.67.

@@

```{r normal-diff, fig.cap="Ridge plots of raw wpd is shown for N(0,1) and N(5,1) distribution. The densities change across different facet and x levels but look same for the two distributions, which implies wpd value is unaffected by the change is mean value of the normal distribution"}
knitr::include_graphics(here::here("simulations/null_design/figs/normal_ridge_nxbynfacet_wpd_N01.png"))
```

```{r gamma-diff, fig.cap="Ridge plots of raw wpd is shown for G(0.5,1) and G(2,1) distribution. The densities change across different facet and x levels and also for the two distributions, which implies wpd value is affected by the change in location value when distributions are not normal."}
knitr::include_graphics(here::here("simulations/null_design/figs/gamma_ridge_nxbynfacet.png"))
```

<!-- ### Choice of alternate designs -->

<!-- A normal distribution is taken for this purpose. We would calibrate the values of $WPD$ for different designs illustrated in Section \ref{sec:idea}. -->

<!-- $$\mu_{j.} = \mu + j\omega$$ -->
<!-- or, $$\mu_{.k} = \mu + k\omega$$ where,    -->
<!-- $j$ and $k$ are the index of the x and facet category respectively  -->
<!-- $\mu$ is the mean of the first category and $\omega$ is the increment from the starting value. -->

<!-- mean = 0 -->
<!-- range_mean = c(0, 1, 3,  5, 7, 15, 20) -->
<!-- sd = 1 -->
<!-- range_sd = c(1, 3,  5, 7, 15, 20) -->
<!-- range_w =  c(1, 2, 3, 4, 5) -->
<!-- range_lambda = seq(0.1, 0.9, 0.05) -->

@@

```{r tuning-one-omega, fig.caption = "WPD from two designs are plotted for different values of lambda for different x and facet categories. For omega = 1, the designs intersect for 0.6<lamba<=0.75, whereas for higher omega, design intersects at lambda = 0.5"}
knitr::include_graphics(here::here("simulations/tuning_param/figs/fixed_omega.png"))
```
